### 2024-06-02 2024-5-13/sections/implementation.tex
experiments

We implemented the procedures and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen} on top of OSTRICH, resulted to a string solver called $\ostrichrecl$. 
%
In this section, we evaluate the performance of $\ostrichrecl$ on three benchmark suites, that is, RegCoL, AutomatArk, and NestC. In the sequel, we first describe the three benchmark suites as well as the experiment setup. Then we present the experiment results. We evaluate the performance and correctness of our solver against the state-of-the-art string constraint solvers, including CVC5 \cite{cvc5}, Z3seq \cite{z3seq}, Z3str3 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH \cite{CHL+19}. We also compare $\ostrichrecl$ with several variants of it, to justify the technical choices made in Section~\ref{sec:algorithm} and evaluate the effectiveness of the optimizations in Section~\ref{sec:heuristic}-\ref{sec-opt-sol-gen}.

@@

\medskip
\noindent
\emph{Experiment setup.}
All experiments are conducted on CentOS Stream release 8 with 4 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory. We use the \textsc{zaligvinder} framework \cite{zaligvinder_2021} to execute the experiments, with a timeout of 60s for each instance.

@@

\subsection{Performance evaluation}\label{subsec:overall_eval}

@@

\subsection{Empirical justification of the technical choices and optimizations}\label{subsec:size_reduction_eval}
We also do experiments to evaluate the effectiveness of the automata size-reduction techniques for register-representable regexes, that is, Step 2 of Section~\ref{subsec:cefadec}. We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. Finally, we carry out experiment on the NestC benchmarks to justify the optimizations of Section~\ref{sec:heuristic} for non-register-representable regexes.
\subsubsection{Empirical justification of the technical choices}
%We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
%Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed. 
We compare $\ostrichrecl$ with its variant  ${\rm +NUXMV}$. ${\rm +NUXMV}$  is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the nonemptiness of $\cefadec$.

The experiment results can be found in Table~\ref{tab:results_heuristic}. We can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than ${\rm +NUXMV}$. Therefore, the decision procedure in Section~\ref{subsec:cefadec} is more efficient to solve the $\cefadec$ problem than nuXmv. 
\begin{table}
  \import{tables}{table_heuristics.tex}
  \caption{Empirical justification of the technical choices and optimizations}\label{tab:results_heuristic}
\end{table}

\subsubsection{Empirical justification of the optimizations for register-representable regexes}
We compare $\ostrichrecl$ with its variant ${\rm -ASR}$.  ${\rm -ASR}$ is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 of Section~\ref{subsec:cefadec}). 
The experiment results can be found in Table~\ref{tab:results_heuristic}. We can see that $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than ${\rm -ASR}$. Therefore,  the automata size-reduction technique indeed plays an essential role in the performance improvement.

\subsubsection{Empirical justification of the optimizations for non-regesiter-representable regexes} 
We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$. ${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting. ${\rm -COMP}$ is obtained by removing the heuristic for complement on counting operators. ${\rm -FIND}$ is obtained by removing the heuristic for finding the accepted word of the automaton.

@@

>>>>

We implemented the procedures and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen} on top of OSTRICH, resulted to a string solver called $\ostrichrecl$. 
%
In this section, we evaluate the performance of $\ostrichrecl$ on three benchmark suites, that is, RegCoL, AutomatArk, and NestC. In the sequel, we first describe the three benchmark suites as well as the experiment setup. Then we present the experiment results. We evaluate the performance and correctness of our solver against the state-of-the-art string constraint solvers, including CVC5 \cite{cvc5}, Z3seq \cite{z3seq}, Z3str3 \cite{Z3-str3}, Z3str3RE \cite{BD+23}, and OSTRICH \cite{CHL+19}. We also compare $\ostrichrecl$ with several variants of itself, to evaluate the effectiveness of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}.

@@

\medskip
\noindent
\emph{Experiment setup.}
All experiments are conducted on CentOS Stream release 8 with 4 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory. We use the \textsc{zaligvinder} framework \cite{zaligvinder_2021} to execute the experiments, with a timeout of 60 seconds per instance.

@@

\subsection{Performance evaluation against the other solvers}\label{subsec:overall_eval}

@@

\subsection{Empirical evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}-\ref{sec-opt-sol-gen}}\label{subsec:size_reduction_eval}

At first, we do experiments to evaluate the effectiveness of the automata size-reduction techniques (i.e. Step 2) in Section~\ref{sec:algorithm}. Then we justify our technical choices of reducing the satisfiability problem to that of LIA formulas and resort to the SMT solvers to solve them. Specifically, we compare $\ostrichrecl$ with a variant where the nuXmv model checker like \cite{atva2020} is used to solve the $\cefadec$ problem. 
%
%We practically answer why we choose LIA formula to solve the nonemptiness problem instead of using the nuXmv model checker like \cite{atva2020}. 
We also evaluate the effectiveness of the optimizations in Section~\ref{sec:heuristic}, i.e. the optimizations for the nesting of counting operators as well as the nesting of counting operators and a complement operator. Finally, we evaluate the effectiveness of the optimizations for the model generation in Section~\ref{sec-opt-sol-gen}.

%Finally, we carry out experiment on the NestC benchmarks to justify the optimizations of Section~\ref{sec:heuristic} for non-register-representable regexes.
%\subsubsection{Empirical justification of the technical choices}
%We also do experiments to evaluate the effectiveness of the automata size-reduction techniques, that is, Step 2 in Section~\ref{subsec:cefadec}. 
%Let us use $\ostrichrecl_{\rm -SIMP}$ to denote $\ostrichrecl$ with the size-reduction techniques removed.

\paragraph*{Empirical evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}
We compare $\ostrichrecl$ with its variant  $\ostrichrecl_{\rm +NUXMV}$, which is obtained from $\ostrichrecl$ by using the nuXmv model checker to solve the $\cefadec$ problem. Moreover, we also compare $\ostrichrecl$ with its variant $\ostrichrecl_{\rm -ASR}$, which is obtained from $\ostrichrecl$ by removing the automata size-reduction technique (i.e. Step 2 in Section~\ref{subsec:cefadec}).

The experiment results can be found in Table~\ref{tab:results_algorithm}. From the results, we can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than $\ostrichrecl_{\rm +NUXMV}$. 
Therefore, the technical choice in Section~\ref{sec:algorithm} where LIA formulas are computed and then solved by the SMT solvers is reasonable, since $\ostrichrecl$ with this technical choice is more efficient than $\ostrichrecl_{\rm +NUXMV}$, where nuXmv is used to solve the $\cefadec$ problem. 
%
Moreover, $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than $\ostrichrecl_{\rm -ASR}$. 
From the results, we can see that the automata-size reduction technique indeed plays an important role for the performance improvement. 
%
\begin{table}
  \import{tables}{table_algorithm.tex}
  \caption{Evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}\label{tab:results_algorithm}
\end{table}

%\subsubsection{Empirical justification of the optimizations for register-representable regexes}

\zhilin{stopped here}

\paragraph*{Evaluation of the optimizations in Section~\ref{sec:heuristic}}
%
%\subsubsection{Empirical evaluation of the optimizations for non-regesiter-representable regexes} 
We also compare the performance of $\ostrichrecl$ with its variants ${\rm -NEST}$, ${\rm -COMP}$, ${\rm -FIND}$. ${\rm -NEST}$ is obtained from $\ostrichrecl$ by removing the heuristic for nested counting. ${\rm -COMP}$ is obtained by removing the heuristic for complement on counting operators. ${\rm -FIND}$ is obtained by removing the heuristic for finding the accepted word of the automaton.

\begin{table}
  \import{tables}{table_heuristics.tex}
  \caption{Evaluation of the optimizations in Section~\ref{sec:heuristic}}\label{tab:results_heuristic}
\end{table}

@@

\paragraph*{Evaluation of the optimizations in Section~\ref{sec-opt-sol-gen}}
